%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://nicolascejas.online/}{\Huge Nicolas Cejas}} & Email: \href{mailto:nicocejas@gmail.com}{nicocejas@gmail.com}\\
  \href{https://nicolascejas.online/}{nicolascejas.online} & Mobile: \href{tel:+34604857281}{+34 604 857 281} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Clarika Software + Innovation }{ DAC - Canada}
      {Ssr. Software Developer}{Nov 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Lanchpad}
          { Contributed to the upgrade of a significant legacy project, working 
on the back-end with .NET Framework and the front-end with Razor 
and React. I notably improved numerous reports, significantly 
increasing efficiency.}
        \resumeItem{Login and Permissions System}
          {Actively 
participated in the back-end development, focused 
on security, employing .NET 8 and Cosmos DB for advanced user 
permission management.}
      \resumeItemListEnd


    \resumeSubheading
      {PriceWaterhouseCoopers}{PwC, USA}
      {Ssr. Software Developer }{June 2020 -- November 2021 }
      \resumeItemListStart
        \resumeItem{Hub of Taxes}
          {Tax API project, leveraging .NET Core and  Azure Cloud technologies (Azure Functions, Service Bus, Azure SQL) 
            to create a centralized API hub for optimizing tax processes.}
        \resumeItem{Internal CRM System}
          { Utilized 
Microsoft Razor Pages, HTML/CSS, and JavaScript for front-end, 
and .NET Core with SQL for back-end, enhancing user experience 
and system customization.}
       
      \resumeItemListEnd

    \resumeSubheading
      {Accion Point Group}{Argentina}
      {Software Developer}{April 2018 - June 2020 }
      \resumeItemListStart
        \resumeItem{Hardware Incubator}
          { Engineered a robust desktop agent using WinForm and .NET Framework for a hardware incubator project, 
          enabling seamless communication via USB, TCP, and IP through the MODBUS protocol}
        \resumeItem{Bantotal}
          { I led the technical integration of a core  banking system, using C\#, 
          RESTSOAP APIs, working with SQL and Oracle databases to extend functionalities and enhance communication 
          with external systems }
      \resumeItemListEnd


  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Universidad Tecnologica Nacional UTN FRSF}{Santa Fe, Argentina}
      {Information Systems Engineer}{}
    \resumeSubheading
      {Macagno, Technical School}{Santa Fe, Argentina}
      {Technician in Organizational Management} {}
  \resumeSubHeadingListEnd




%
%--------SKILLS------------
\section{Hard Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languajes}
      {C\# | Javascript | HTML/CSS | SQL}
    \resumeSubItem{Frameworks}
      {NET - NET Framework -- React -- WEB API MVC}
    \resumeSubItem{Tools}
      {Unit Test - ORM: Dapper/Entity Framework - Azure Cloud: Azure Functions, Service Bus }
  \resumeSubHeadingListEnd



%-------------------------------------------

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal Card Page}
      {Personal web page using Next.js and MUI.}
      \resumeSubItem{Super minihammer}
      {Personal app to handle daily tasks. Build as monorepo with Netxjs, NET8, Entity Framework, Docker}
  \resumeSubHeadingListEnd
  
\end{document}
